---
title: "Variables"
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, echo = FALSE)
summaries <- WorkInData::wid_variables()
```
Reformatted into parquet files partitioned by `survey` and `year` in 453 parts:

**Variables**: 16

**Observations**: 232,121,775

**Size**: 1.59 GB


# Sample

## Survey

Initials of the source survey.

**ID**: survey

**Type**: string

**Missing**: 0

**Value Summary**:

```{r}
s <- summaries[["survey"]]
knitr::kable(data.frame(
  Level = names(s$summary$value_summary), Count = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

## Year

Year in which the survey was conducted.

**ID**: year

**Type**: int32

**Missing**: 0

**Value Summary**:

```{r}
s <- summaries[["year"]]
knitr::kable(data.frame(
  Level = names(s$summary$value_summary), Count = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

## Survey Year

Survey year for panel construction.

**ID**: survey_year

**Type**: int16

**Missing**: 135,278,433

**Value Summary**:

```{r}
s <- summaries[["survey_year"]]
knitr::kable(data.frame(
  Level = names(s$summary$value_summary), Count = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

## Sampling Weight

Weight provided in the source survey; either cross-sectional or panel.

**ID**: wgt

**Type**: float

**Missing**: 1,167,729

**Value Summary**:

```{r}
s <- summaries[["wgt"]]
knitr::kable(data.frame(
  Feature = names(s$summary$value_summary), Value = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

# Location

## Country

Country in which the survey was conducted.

**ID**: country

**Type**: string

**Missing**: 0

**Value Summary**:

```{r}
s <- summaries[["country"]]
knitr::kable(data.frame(
  Level = names(s$summary$value_summary), Count = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

## Rural

Whether the respondent's location is classified as rural.

**ID**: rural

**Type**: bool

**Missing**: 56,522,713

**Value Summary**:

```{r}
s <- summaries[["rural"]]
knitr::kable(data.frame(
  Level = names(s$summary$value_summary), Count = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

# Individual

## Individual ID

Individual identifier.

**ID**: id_ind

**Type**: string

**Missing**: 0

**Value Summary**:

```{r}
s <- summaries[["id_ind"]]
knitr::kable(data.frame(
  Feature = names(s$summary$value_summary), Value = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

## Age

Respondents age.

**ID**: age

**Type**: int32

**Missing**: 628,673

**Value Summary**:

```{r}
s <- summaries[["age"]]
knitr::kable(data.frame(
  Feature = names(s$summary$value_summary), Value = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

## Sex

Whether the respondent reported being female.

**ID**: sex

**Type**: bool

**Missing**: 576,976

**Value Summary**:

```{r}
s <- summaries[["sex"]]
knitr::kable(data.frame(
  Level = names(s$summary$value_summary), Count = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

## Marital Status

Marital status of the respondent.

**ID**: marital_status

**Type**: string

**Missing**: 14,572,489

**Value Summary**:

```{r}
s <- summaries[["marital_status"]]
knitr::kable(data.frame(
  Level = names(s$summary$value_summary), Count = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

## Education

Highest level of education completed.

**ID**: education

**Type**: string

**Missing**: 22,597,122

**Value Summary**:

```{r}
s <- summaries[["education"]]
knitr::kable(data.frame(
  Level = names(s$summary$value_summary), Count = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

# Household

## Children Under 5

Number of children under 5 within the household.

**ID**: n_child_5

**Type**: int16

**Missing**: 59,692,991

**Value Summary**:

```{r}
s <- summaries[["n_child_5"]]
knitr::kable(data.frame(
  Feature = names(s$summary$value_summary), Value = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

# Work

## Working

Whether the respondent worked in the reference period.

**ID**: work

**Type**: bool

**Missing**: 35,134,187

**Value Summary**:

```{r}
s <- summaries[["work"]]
knitr::kable(data.frame(
  Level = names(s$summary$value_summary), Count = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

## Looking for Work

Whether the respondent is looking for work, given that they are not currently working.

**ID**: work_search

**Type**: bool

**Missing**: 143,080,517

**Value Summary**:

```{r}
s <- summaries[["work_search"]]
knitr::kable(data.frame(
  Level = names(s$summary$value_summary), Count = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

# Job

## Industry Classification

Industry classification (International Standard Industrial Classification; ISIC).

**ID**: main_job_ind

**Type**: string

**Missing**: 128,471,814

**Value Summary**:

```{r}
s <- summaries[["main_job_ind"]]
knitr::kable(data.frame(
  Feature = names(s$summary$value_summary), Value = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

## Job Activity Category

If working, the industry sector of the job; otherwise, either unemployed or out of workforce.

**ID**: main_activity

**Type**: string

**Missing**: 47,387,122

**Value Summary**:

```{r}
s <- summaries[["main_activity"]]
knitr::kable(data.frame(
  Level = names(s$summary$value_summary), Count = unname(unlist(s$summary$value_summary))
), row.names = FALSE, digits = 4, format.args = list(big.mark = ",", scientific = FALSE))
```

